---
title: "R Notebook"
output:
  html_notebook:
    df_print: paged
---

/

#### Here is the little story I realized after doing a brief study about the texts of 58 U.S. presidents' inaugural speeches from George Washington to that of Donald Trump. I focused most on some presidents who won the presidential election more than one term and another two “special” presidents named Grover Cleveland and Franklin D. Roosevelt respectively. I got the number 0.4 by simple calculation, which indicates that there were approximately 40% of presidents who served for another term of United States. 

#### By doing the analysis about each presidents’ length of words in their inaugural speeches, I saw the trend that if presidents won more than one term, most of them tended to speak less than or almost the same number of words in the next term’s inaugural speeches. Few reelected presidents spoke more than their first term’s inaugural speeches. I guess the reason is that, as citizens get more familiar with the current president and if they really admire him, the positive relationship will build between people and their president. When the next election comes, the president can still win without saying so much.

#### Besides, I found two special cases about reelected presidents. One is Grover Cleveland who was the only president to leave the White House and returned for a second term four years later. Moreover, after searching online, I knew that he won the popular vote for three presidential elections which were in year 1884, 1888, and 1892. During the era of Republican party domination, he was Democrats to be elected as U.S. president. The other one is Franklin D. Roosevelt who was the only president in the American history that won four consecutive presidential elections. This is the strong evidence to show that how eminent he was to work as the president. 

#### Based on all information I collected before, I tried to analyze what kinds of topics presidents liked to say in their inaugural speeches. Using topic modeling, classifying 15 topics from “Industry” to “Patriot”, I mainly focused on five categories that I though citizens cared about most, which were "Equality", "Protection", "HumanRight", "Freedom" and "Welfare" respectively. I only plotted graphs for two special presidents Grover Cleveland and Franklin D. Roosevelt. For the same president in different two terms, the weighted number for five topics in their speeches were almost the same, which means fields both dedicated to did not change so much in different years.  Moreover, the order of topics was almost the same for the two except only slightly different weighted numbers. The order from more to less was "Welfare", "Freedom”, “HumanRight”, “Protection" and "Equality". Both presidents delivered speeches mainly about welfare in those five ones. I believed this is true because welfare is a typical indicator to represent people’s happiness and living standard. I can pretty sure to say every president wants to build a harmonious country for their citizens.  

/

##### Below is my specific study
```{r, message=FALSE, warning=FALSE}
# Load libraries:
library(rvest)
library(tibble)
library(sentimentr)
library(gplots)
library(ggplot2)
library(dplyr)
library(tm)
library(syuzhet)
library(factoextra)
library(scales)
library(RANN)
library(topicmodels)
library(qdap)

# Function is copied from this website below
# https://github.com/TZstatsADS/ADS_Teaching/blob/master/Tutorials/wk2-TextMining/lib/plotstacked.R
source("../lib/plotstacked.R")

# Function is copied from this website below
# https://github.com/TZstatsADS/ADS_Teaching/blob/master/Tutorials/wk2-TextMining/lib/speechFuncs.R
source("../lib/speechFuncs.R")
```


###### This notebook was prepared with the following environmental settings
```{r}
print(R.version)
```

```{r}
# Load the data
inaug.date <- read.table("../data/InauguationDates.txt", header = TRUE, stringsAsFactors = FALSE, sep = "\t")
inaug.info <- read.csv("../data/InaugurationInfo.csv", 1, stringsAsFactors = FALSE)
```

/

### Presidents who left the White House and returned for a second term four years later:

/
```{r}
inaug.date[inaug.date$FIRST == "" & inaug.date$SECOND != "", ]$PRESIDENT
```

/

### Presidents who held a post more than two terms:

/
```{r}
inaug.info$President[inaug.info$Term > 2]
```


###### Check two dataframes to see whether they can combined together
```{r}
# Check two dataframes' president variable consistency
p.info <- unique(inaug.info$President)
p.date <- inaug.date$PRESIDENT
setdiff(p.info, p.date)
setdiff(p.date, p.info)
inaug.date.del <- inaug.date[inaug.date$PRESIDENT != "John Tyler"& inaug.date$PRESIDENT != "Millard Fillmore"& 
                               inaug.date$PRESIDENT != "Andrew Johnson"& inaug.date$PRESIDENT != "Chester Arthur"&
                               inaug.date$PRESIDENT != "Gerald R. Ford", ]

# Check two dataframes' term consistency 
p.info2 <- unique(inaug.info[inaug.info$Term > 1, ]$President)
p.date2 <- inaug.date.del[inaug.date.del$SECOND != "", ]$PRESIDENT
setdiff(p.info2, p.date2)
setdiff(p.date2, p.info2)
inaug.date.del[inaug.date.del$PRESIDENT == "Theodore Roosevelt", "SECOND"] <- ""
inaug.date.del[inaug.date.del$PRESIDENT == "Calvin Coolidge", "SECOND"] <- ""
inaug.date.del[inaug.date.del$PRESIDENT == "Harry S. Truman", "SECOND"] <- ""
inaug.date.del[inaug.date.del$PRESIDENT == "Lyndon B. Johnson" , "SECOND"] <- ""
```


###### Build inaug.list with inaug.info and two new vectors "Date", "Reelection" 
```{r}
# Create the Date vector
Date <- NULL
count <- 1
for (i in 1:nrow(inaug.date.del)) {
  for (j in 2:5) {
    Date[count] <- inaug.date.del[i,j]
    count <- count + 1
  }
}
Date <- Date[Date != ""]

# Build the new dataframe that combines inaug.info dataframe with the new vector Date
inaug.list <- data.frame(inaug.info, Date = Date)

# Add the created Reelection vector to inaug.list
inaug.list$Reelection <- "No"
n <- nrow(inaug.list)-1
for (index in 1:n) {
  if (inaug.list$Term[index+1] > inaug.list$Term[index]) {
  inaug.list$Reelection[index+1] <- "Yes"
  inaug.list$Reelection[index] <- "Yes"
  }
}

# Assign "No" to special cases
con <- inaug.list$President == "Grover Cleveland - I"| inaug.list$President == "Benjamin Harrison"|
  inaug.list$President == "Grover Cleveland - II" 
inaug.list[con, "Reelection"] <- "No"
```

/

### The proportion of reelected presidents:

/
```{r}
ree.num <- length(unique(inaug.list[inaug.list$Reelection == "Yes", ]$President))
total.num <- length(unique(inaug.list$President))
prop <- ree.num/total.num
prop
```

/

### The number of words in different terms for reelected presidents:

/
```{r}
ree.df <- inaug.list[inaug.list$Reelection == "Yes", c("President", "Term", "Words")]
ree.df$Term <- factor(ree.df$Term)
ree.df$Words <- as.numeric(ree.df$Words)
ggplot(ree.df[1:10, ], aes(factor(President), Words, fill = Term)) +  
  geom_bar(stat="identity", position = "dodge") + 
  labs(title = "The number of words in different terms for reelected presidents", 
       x = "Presidents", y = "The number of words")
ggplot(ree.df[11:22, ], aes(factor(President), Words, fill = Term)) + 
  geom_bar(stat="identity", position = "dodge") + 
  labs(title = "The number of words in different terms for reelected presidents", 
       x = "Presidents", y = "The number of words")
ggplot(ree.df[23:34, ], aes(factor(President), Words, fill = Term)) + 
  geom_bar(stat="identity", position = "dodge") + 
  labs(title = "The number of words in different terms for reelected presidents", 
       x = "Presidents", y = "The number of words")
```


###### Most of codes below are built based on the website "https://github.com/TZstatsADS/ADS_Teaching/blob/master/Tutorials/wk2-TextMining/doc/wk2-Tutorial-TextMining.Rmd" 

###### Get inaugural speeches from the website "http://www.presidency.ucsb.edu/inaugurals.php"
```{r}
# Get speeches urls
main.page <- read_html(x = "http://www.presidency.ucsb.edu/inaugurals.php")
inaug.url <- f.speechlinks(main.page)
inaug.url <- inaug.url[-nrow(inaug.url), ]

# Add the new vector Urls to inaug.list
inaug.list$Urls <- inaug.url$urls

# Loop over each row in inaug.list
inaug.list$Fulltext <- NA
for(i in 1:nrow(inaug.list)) {
    text <- read_html(inaug.list$Urls[i]) %>% 
    html_nodes(".displaytext") %>% 
    html_text() 
    inaug.list$Fulltext[i] <- text
}
```


###### Create the sen.list dataframe
```{r, message=FALSE, warning=FALSE}
# Loop to assign a consecutive id to each sentence
sen.list <- NULL
for(i in 1:nrow(inaug.list)){
  Sentences <- sent_detect(inaug.list$Fulltext[i], endmarks = c("?", ".", "!", "|",";"))
  if(length(Sentences)>0){
    sen.list <- rbind(sen.list, cbind(inaug.list[i,-ncol(inaug.list)],
                                   Sentences=as.character(Sentences), Sen.id=1:length(Sentences)))
  }
}
```

```{r}
# Build a corpus of sentence Snipets
corpus <- sen.list[2:(nrow(sen.list)-1), ]
sen.pre <- sen.list$Sentences[1:(nrow(sen.list)-2)]
sen.post <- sen.list$Sentences[3:(nrow(sen.list)-1)]
corpus$Snipets <- paste(sen.pre, corpus$Sentences, sen.post, sep=" ")
rm.rows <- (1:nrow(corpus))[corpus$Sen.id==1]
rm.rows <- c(rm.rows, rm.rows-1)
corpus <- corpus[-rm.rows, ]
```

```{r}
# Text mining
docs <- Corpus(VectorSource(corpus$Snipets))
```

```{r}
# Text processing
docs <- tm_map(docs, stripWhitespace) #get rid of whitespace
docs <- tm_map(docs, removePunctuation) #get rid of punctuation
docs <- tm_map(docs, removeNumbers) #get rid of digits
docs <- tm_map(docs, removeWords, stopwords("english")) #get rid of stopwords
docs <-tm_map(docs,content_transformer(tolower)) #get rid of likely problematic symbols
docs <- tm_map(docs,stemDocument) #Stem document
```

```{r}
# Build matrices
dtm <- DocumentTermMatrix(docs)
total <- apply(dtm , 1, sum)
dtm <- dtm[total>0, ]
corpus <- corpus[total>0, ]
```

```{r}
# Parameters about Gibbs sampling
burnin <- 4000
iter <- 2000
thin <- 500
seed <-list(2003,5,63,100001,765)
nstart <- 5
best <- TRUE

# Topics numbers
k <- 15

# LDA 
ldaout<-LDA(dtm, k, method="Gibbs", control=list(nstart=nstart, seed = seed, best=best,
                                                 burnin = burnin, iter = iter, thin=thin))
```

```{r}
l.topics <- as.matrix(topics(ldaout)) # Convert to topics
l.terms <- as.matrix(terms(ldaout,10)) # Top 10 terms in each topic
l.terms
prop.topics <- as.data.frame(ldaout@gamma) # Probabilities about assigning topics
```

```{r}
# Assign a hashtag to each topic
htag <- c("Industry", "Legislation", "Spirit", "Opinion", "Equality", "Wish", "Protection", "HumanRight", 
          "Government", "Freedom", "Citizen", "Welfare", "MilitaryForce", "Confidence", "Patriot")
corpus$ltopic <- as.vector(l.topics)
corpus$lhtag <- htag[l.topics]
colnames(prop.topics) <- htag
corpus.df <- cbind(corpus, prop.topics)
```

/

### Topics weighted plot for president Grover Cleveland:

/
```{r}
t.plot <- c(5, 7, 8, 10, 12) # Choose specific topics
print(htag[t.plot])

inaug.df <- tbl_df(corpus.df)%>%filter(File=="GroverCleveland-I", Term==1)%>%select(Sen.id, Industry:Patriot)
inaug.df <- as.matrix(inaug.df)
inaug.df[,-1] <- replace(inaug.df[,-1], inaug.df[,-1] < 1/15, 0.001) 
inaug.df[,-1] <- f.smooth.topic(x=inaug.df[,1], y=inaug.df[,-1])
plot.stacked(inaug.df[,1], inaug.df[,t.plot+1], main="Grover Cleveland's Term1 Inaugural Speech", 
             xlab="Sentences ID", ylab="Topics")

inaug.df <- tbl_df(corpus.df)%>%filter(File=="GroverCleveland-II", Term==2)%>%select(Sen.id, Industry:Patriot)
inaug.df <- as.matrix(inaug.df)
inaug.df[,-1] <- replace(inaug.df[,-1], inaug.df[,-1] < 1/15, 0.001) 
inaug.df[,-1] <- f.smooth.topic(x=inaug.df[,1], y=inaug.df[,-1])
plot.stacked(inaug.df[,1], inaug.df[,t.plot+1], main="Grover Cleveland's Term2 Inaugural Speech",
             xlab="Sentences ID", ylab="Topics")
```

/

### Topics weighted plot for president Franklin D. Roosevelt:

/
```{r}
inaug.df <- tbl_df(corpus.df)%>%filter(File=="FranklinDRoosevelt", Term==1)%>%select(Sen.id, Industry:Patriot)
inaug.df <- as.matrix(inaug.df)
inaug.df[,-1] <- replace(inaug.df[,-1], inaug.df[,-1] < 1/15, 0.001) 
inaug.df[,-1] <- f.smooth.topic(x=inaug.df[,1], y=inaug.df[,-1])
plot.stacked(inaug.df[,1], inaug.df[,t.plot+1], main="Franklin D. Roosevelt's Term1 Inaugural Speech",
             xlab="Sentences ID", ylab="Topics")

inaug.df <- tbl_df(corpus.df)%>%filter(File=="FranklinDRoosevelt", Term==2)%>%select(Sen.id, Industry:Patriot)
inaug.df <- as.matrix(inaug.df)
inaug.df[,-1] <- replace(inaug.df[,-1], inaug.df[,-1] < 1/15, 0.001) 
inaug.df[,-1] <- f.smooth.topic(x=inaug.df[,1], y=inaug.df[,-1])
plot.stacked(inaug.df[,1], inaug.df[,t.plot+1], main="Franklin D. Roosevelt's Term2 Inaugural Speech",
             xlab="Sentences ID", ylab="Topics")
```


/

#### Code Reference

https://github.com/TZstatsADS/ADS_Teaching/blob/master/Tutorials/wk2-TextMining/lib/plotstacked.R 

https://github.com/TZstatsADS/ADS_Teaching/blob/master/Tutorials/wk2-TextMining/lib/speechFuncs.R

http://www.presidency.ucsb.edu/inaugurals.php

https://github.com/TZstatsADS/ADS_Teaching/blob/master/Tutorials/wk2-TextMining/doc/wk2-Tutorial-TextMining.Rmd

/














